Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2017-11-03 paper/galsize_paper.tex
Revisions to 5.3.2

First, the bottom right panel of Figure \ref{fig:colorclustering} indicates that the size of the bulge has only a tenuous connection to the properties of its parent dark matter halo.\footnote{Strictly speaking, the size of the bulge could in principle be closely connected to any number of dark matter halo properties, so long as those halo properties do not significantly impact two-point clustering.} Second, for disk-dominated galaxies, the observed $\rhalf-$dependent clustering suggests that at fixed $\mstar,$ the size of the disk is strongly correlated with whether or not the galaxy is a satellite.

%Previous studies of large-scale structure measured by SDSS indicate that morphological type has a significant influence on galaxy clustering \citep{skibba_etal08}. Because morphology is covariant with star-formation rate (SFR) and $\rhalf,$ accounting for this dependency will require simultaneously modeling each of these variables.

%To date, such a task has been beyond the purview of empirical models. However, recent progress has substantially improved the richness of the predictions that galaxy-halo models are capable of \citep{becker15,cohn17,moster_etal17}. This new class of models has accomplished this by empirically modeling star-formation rate, and then integrating SFR along each halo's history to differentially build up stellar mass.\footnote{This approach towards predicting $\mstar$ is thus mathematically akin to traditional semi-analytic models, although \citet{becker15} have retained the empirical modeling prioritization of simplicity and computational efficiency.} We are currently extending this new class of models to differentially build up the disk and bulge across cosmic time. In addition to treating the multi-dimensional nature of the problem, this also allows us to use data at higher redshift in a self-consistent manner.

>>>>

First, the bottom right panel of Figure \ref{fig:colorclustering} indicates that the size of the bulge has only a tenuous connection to the properties of its parent dark matter halo.\footnote{Strictly speaking, the size of the bulge could in principle be closely connected to any number of dark matter halo properties, so long as those halo properties do not significantly impact two-point clustering.} Second, for disk-dominated galaxies, the observed $\rhalf-$dependent clustering suggests that at fixed $\mstar,$ the size of the disk is strongly correlated with whether or not the galaxy is a satellite. Our analysis complements \citet{weinmann_etal08}, who reach the same conclusions based on a study of galaxy group catalogs. These findings imply that bulge prominence is intimately connected with the quenching of star-formation, but that there is wide variation in star-formation histories amongst disk-dominated galaxies, in agreement with numerous previous findings \citep[see, e.g.,][]{woo_etal15,font_etal17}.

Previous studies of large-scale structure measured by SDSS indicate that morphological type has a significant influence on galaxy clustering \citep{skibba_etal08}. Because morphology is covariant with star-formation rate (SFR) and $\rhalf,$ accounting for this dependency will require simultaneously modeling each of these variables. Historically, such a task has been beyond the purview of empirical models. However, recent progress has substantially improved the richness of the predictions that galaxy-halo models are capable of \citep{becker15,cohn17,moster_etal17}. This new class of models has accomplished this by empirically modeling star-formation rate, and then integrating SFR along each halo's history to differentially build up stellar mass. We are currently extending this new class of models to differentially build up the disk and bulge across cosmic time using computationally efficient empirical modeling methods. In addition to treating the multi-dimensional nature of the problem, this will allow us to use data at higher redshift in a self-consistent manner.
